Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-07-27 Manuscript/proto-manuscript.tex
MS: wrote section Simulation details

\todo{To be written}

\subsubsection{Simulations with cationic surfactants}
Automated topoly builder \cite{malde11} was first used to create pdb structure of
dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$, molecule.
The AmberTools \cite{amber} was then used to generate the Amber force field
parameters from the pdb file. These were converted to Gromacs format by using
acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond the corresponding segments in Lipid14 \cite{dickson14}.
The surfactants were randomly mized with lipids to form bilayer structures with
mole fractions 10\%, 20\%, 30\%, 42\% and 50\% of surfctant in POPC bilayer.
Simulation parameters and force field for POPC was already used and
described previously \cite{catte16} and were downloaded from \cite{lipid14POPC0mMNaClfiles}.
The systems were simulated 100-200~ns at 313K and the first 20~ns of the trajectories
were excluded from the analysis as an equilibration period.
The simulations were ran with Gromacs 5~\cite{abraham15}. 
Simulation trajectories and parameters are available at \cite{??} \todo{To be uploaded to Zenodo}.

>>>>

The simulated systems consisted of 1-Palmitoyl-2-oleoylphosphatidylcholine (POPC) bilayer and an aqueous salt solutions of varying concentrations.
Water molecules were described by OPC3 model \cite{Izadi16}.
In order to test transferability of the newly developed ECC-Lipids model, 
we also performed several additional simulations with water models 
OPC \cite{Izadi14}, SPC/E \cite{Berendsen1987} and TIP4p/2005 \cite{Abascal2005}
presented in Supporting Information (SI). 
We used ECC-ions model for ions. \cite{jungwirth17-new-paper-to-be-published, kohagen16, Pluharova2014} % cite order: [Ca_2s, Na_s, Cl_2s]
Classical molecular dynamics simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4).  
The simulation settings used in this work are 
are summarized in Table \ref{tbl:mdpar}, 
and they are based on previously used settings in \cite{catte16} available at \cite{lipid14POPC0mMNaClfiles}. 
Simulation trajectories and parameters are available at \cite{??} \todo{To be uploaded to Zenodo}.

\begin{table}[btp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & 100~ns  \\
    simulation time     & 200~ns  \\
    temperature         & 313~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only Hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}

\subsubsection{Simulations with cationic surfactants}
Automated topology builder \cite{malde11} was first used to create the structure of
dihexadecyldimethylammonium bromide, C$_{12}$Cl$_{16}$$^+$N2C$_1$Br$^-$, molecule.
The code AmberTools \cite{amber} was then used to generate the Amber-type force field
parameters. The parameters were converted to the Gromacs format by using
acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond to their equivalent segments in Lipid14 \cite{dickson14}.
The surfactants were randomly placed among the lipids to form bilayer structures with
mole fractions 10\%, 20\%, 30\%, 42\% and 50\% of surfactant in the POPC bilayer.
